Hyperbolicity of Augmented Links in the Thickened Torus

### 2020-10-06 circlepatterns.tex
fixed captions for figures

\begin{figure}
\includegraphics[width=8cm]{more_pictures/kite.png}
	\caption{The kite of two circles intersecting in a ``normal" circle pattern.}
\end{figure}
\begin{figure}
\includegraphics[width=5cm]{more_pictures/positive_angle.png}
\includegraphics[width=5cm]{more_pictures/negative_angle.png}
	\caption{Kites of a degenerate circle pattern.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=6cm]{more_pictures/kite.png}
	\caption{The quadrangle associated to the edge $e$ between two
		convex faces.}
\end{figure}
\begin{figure}
\includegraphics[height=5cm]{more_pictures/positive_angle.png}
\includegraphics[height=5cm]{more_pictures/negative_angle.png}
	\caption{Left: Quadrangle when $\theta_e$ is small and positive;
		Right: Quadrangle when $\theta_e$ is small and negative,
		so it takes up ``negative area'' (see proof of
		\lemref{l:circpattern_polyhedra}).}
\end{figure}
